There are no small Advantages: Reinforcement learning in near continuous time with Deep RelAtive Mixture of Advantages

### 2019-01-12 paper/icml_drau/framework.tex
advancing...

%! TEX root = icml_drau.tex
\section{Near continuous time reinforcement learning}
\label{sec:continous}
% In this section, a continuous reinforcement learning framework is introduced,
% and it is shown that under this framework, the state-action value function does
% not depend on the action. We further show that in near continous domains, when
% the discretization timestep $\deltat$ is small, the difference in state-action
% value between two different actions in a fixed state is of order $\bigO(\deltat)$.
\TODO{. Main ideas: near continuous time environments (control, mujoco, video games, ...)
There is a time discretization $\deltat$ given by the problem. The uderlying process does not depend of $\deltat$. Need to see what is happening when changing $\deltat$. The problem is invariant to $\deltat$. The quantities we are looking at should be invariant to. The learning procedure should be invariant. Looking at the limits when $\deltat \rightarrow 0$. In simulated environments, changing $\deltat$ only means to change the FPS. In real environments, for example with robots, this could mean changing the quality of the sensors and motors.}

@@

Let assume that we have a Markov Decision Process \TODO{Cite?} $\langle {\cal S}, {\cal A}, T_{\deltat}, r_\deltat, \gamma_\deltat\rangle$. ${\cal S}$ is the state-space, which is supposed to be continuous \TODO{not the good formulation}. The action space is \TODO{todo}.

We assume that the transition is continuous. This means that ... \TODO{todo}. Discussion on the hypothesis, in which environments it is true. Is the condition $\forall \deltat, \forall s, \E[\|s_{k+1} - s_k \||s_k = s] \leq ?$.

In many situations, we can assume that there is an uderlying process:
\begin{equation}
  \label{eq:diffusion}
  ds = F(s, a) + \Sigma(s, a)\dbt
\end{equation}
$F$ is the physics, and $\dbt$ is the noise.

There is convergence to the continuous process when $\deltat \rightarrow 0$.

@@

TODO: Explain $a_t = \pi(s_t)$ deterministic.

>>>>

%! TEX root = icml_drau.tex
\section{Near continuous time reinforcement learning}
\label{sec:framework}
% In this section, a continuous reinforcement learning framework is introduced,
% and it is shown that under this framework, the state-action value function does
% not depend on the action. We further show that in near continous domains, when
% the discretization timestep $\deltat$ is small, the difference in state-action
% value between two different actions in a fixed state is of order $\bigO(\deltat)$.

\TODO{. Main ideas: near continuous time environments (control, mujoco, video games, ...)
There is a time discretization $\deltat$ given by the problem. The uderlying process does not depend of $\deltat$. Need to see what is happening when changing $\deltat$. The problem is invariant to $\deltat$. The quantities we are looking at should be invariant to. The learning procedure should be invariant. Looking at the limits when $\deltat \rightarrow 0$. In simulated environments, changing $\deltat$ only means to change the FPS. In real environments, for example with robots, this could mean changing the quality of the sensors and motors.}

@@

We say that ${\cal M}_\deltat = \langle {\cal S}, {\cal A}, T_{\deltat}, r_\deltat, \gamma_\deltat\rangle$ is a \emph{near-continuous} Markov Decision Process with trajectories $(s_\deltat^k)_{k\in\mathbb{N}}$ if there is a \emph{physical time} $\deltat$ between two observations, and if $(s_\deltat^{k+1})$ is close to $s_\deltat^k$. We assume that the state space ${\cal S}$ is continuous \TODO{True? Ok?}. The action space ${\cal A}$ can be either continuous or discrete \TODO{except in the theorems}.

Many practical Reinforcement Learning problem can be considered as near-continuous: For example, in a simulated physical environment in which the $\deltat$ is fixed by the simulator, or in a real environments, if the agent is a robot.

% , the $\deltat$ is fixed by the sensitivity of the sensors and the reactivity of the motors. We assume that the state space ${\cal S}$ is continuous.

In many situations, we can assume that the agent is actually is following a diffusion process:
\begin{equation}
  \label{eq:diffusion}
  ds = F(s, a)dt + \Sigma(s, a)\dbt
\end{equation}
where $F: {\cal S}\times{\cal A}\rightarrow {\cal S}$ describes the physics of the environment, and $\dbt$ is the noise of the environment. If the environment is deterministic as in classical control theory, or in many usual simulated environments (Mujoco, Gym, ...), we have $\Sigma = 0$.

In this work we only consider deterministic policies $\pi: {\cal S} \rightarrow {\cal A}$. Therefore, the diffusion equation becomes:
\begin{equation}
  \label{eq:diffusion-policy}
  ds = F(s, \pi(s))dt + \Sigma(s, \pi(s))\dbt
\end{equation}

\begin{theorem}
  Assume that $\pi: {\cal S} \rightarrow {\cal A}$ is a continuous and deterministic policy. Let $(s_t)_{t\in\mathbb{R}_+}$ be the continuous process by following \eqref{eq:diffusion}. Let $(s^\deltat_k)$ be the discrete process obtained if the agent only get observations every $\deltat$ \TODO{explain better}. Then:
  \begin{equation}
    \label{eq:conv-traj}
    (s_{\lfloor \frac{t}{\deltat}\rfloor}^\deltat)_{t\in\mathbb{R}_+} \rightarrow_{\deltat \rightarrow 0} (s_t)_{t\in\mathbb{R}_+}
  \end{equation}
  as probability distributions.
\end{theorem}

@@
